\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
Add : table of latency cpu-stressed data (table 4)
Caption of table might need to change

\subsection{Experiment Result}
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/cyclictest_idle.jpg}
\caption{Cyclictest with no stress.}
\label{cyclictest-idle}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/cyclictest_stress.jpg}
\caption{Cyclictest with stress.}
\label{cyclictest-stress}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/x2-idle.png}
\caption{Latency with no stress on Xenomai-2.}
\label{x2-latency-idle}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/x2-cpu.png}
\caption{Latency with stress on Xenomai-2.}
\label{x2-latency-stress}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/x3-idle.png}
\caption{Latency with no stress on Xenomai-3.}
\label{x3-latency-idle}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/x3-cpu.png}
\caption{Latency with stress on Xenomai-3.}
\label{x3-latency-stress}
\end{center}
\end{figure} 
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular}{|l|r|r|r|}
\hline
\multirow{2}{*}{} & \multicolumn{3}{c|}{idle}  \\ \cline{2-4} 
 & \multicolumn{1}{l|}{min} & \multicolumn{1}{l|}{avg} & \multicolumn{1}{l|}{max} \\ \hline
Mainline Linux & 39 & 43 & 1046  \\ \hline
Preempt-RT & 16 & 21 & 52 \\ \hline
Xenomai 2 & 8 & 9 & 41 \\ \hline
Xenomai 3 & 7 & 7 & 35 \\ \hline
 & \multicolumn{3}{c|}{cpu-stressed} \\ \hline
Mainline Linux & 39 & 52 & 1097 \\ \hline
Preempt-RT & 18 & 25 & 62 \\ \hline
Xenomai 2 & 8 & 19 & 45 \\ \hline
Xenomai 3 & 6 & 16 & 37 \\ \hline
\end{tabular}\\
\vspace{4mm} \\
Table 2: cyclictest result on different kernel setups, in \textmu s\\
\vspace{4mm} \\
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular}{|l|c|r|r|}
\hline
\multirow{2}{*}{} & \multicolumn{3}{c|}{user} \\ \cline{2-4} 
 & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} \\ \hline
Xenomai 2 & 8.541 & 9.458 & 34.583 \\ \hline
Xenomai 3 & 8.043 & 8.853 & 33.023 \\ \hline
& \multicolumn{3}{c|}{kernel}      \\ \hline
Xenomai 2 & 6.965 & 7.708 & 27.821 \\ \hline
Xenomai 3 & 5.567 & 6.479 & 25.577 \\ \hline
& \multicolumn{3}{c|}{timer-irq}   \\ \hline
Xenomai 2 & 2.129 & 2.654 & 11.343 \\ \hline
Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
\end{tabular} \\
\vspace{4mm} \\
Table 3: latency result on different kernel setups, in \textmu s\\

>>>>

\subsection{Experiment Result}
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/cyclictest_idle.jpg}
\caption{Cyclictest with no stress.}
\label{cyclictest-idle}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/cyclictest_stress.jpg}
\caption{Cyclictest with stress.}
\label{cyclictest-stress}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/x2-idle.png}
\caption{Latency with no stress on Xenomai-2.}
\label{x2-latency-idle}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/x2-cpu.png}
\caption{Latency with stress on Xenomai-2.}
\label{x2-latency-stress}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/x3-idle.png}
\caption{Latency with no stress on Xenomai-3.}
\label{x3-latency-idle}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{img/x3-cpu.png}
\caption{Latency with stress on Xenomai-3.}
\label{x3-latency-stress}
\end{center}
\end{figure} 
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular}{|l|r|r|r|}
\hline
\multirow{2}{*}{} & \multicolumn{3}{c|}{idle}  \\ \cline{2-4} 
 & \multicolumn{1}{l|}{min} & \multicolumn{1}{l|}{avg} & \multicolumn{1}{l|}{max} \\ \hline
Mainline Linux & 39 & 43 & 1046  \\ \hline
Preempt-RT & 16 & 21 & 52 \\ \hline
Xenomai 2 & 8 & 9 & 41 \\ \hline
Xenomai 3 & 7 & 7 & 35 \\ \hline
 & \multicolumn{3}{c|}{cpu-stressed} \\ \hline
Mainline Linux & 39 & 52 & 1097 \\ \hline
Preempt-RT & 18 & 25 & 62 \\ \hline
Xenomai 2 & 8 & 19 & 45 \\ \hline
Xenomai 3 & 6 & 16 & 37 \\ \hline
\end{tabular}\\
\vspace{4mm} \\
Table 2: cyclictest result on different kernel setups, in \textmu s\\
\vspace{4mm} \\
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular}{|l|c|r|r|}
\hline
\multirow{2}{*}{} & \multicolumn{3}{c|}{user} \\ \cline{2-4} 
 & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} \\ \hline
Xenomai 2 & 8.541 & 9.458 & 34.583 \\ \hline
Xenomai 3 & 8.043 & 8.853 & 33.023 \\ \hline
& \multicolumn{3}{c|}{kernel}      \\ \hline
Xenomai 2 & 6.965 & 7.708 & 27.821 \\ \hline
Xenomai 3 & 5.567 & 6.479 & 25.577 \\ \hline
& \multicolumn{3}{c|}{timer-irq}   \\ \hline
Xenomai 2 & 2.129 & 2.654 & 11.343 \\ \hline
Xenomai 3 & 2.586 & 3.079 & 10.031 \\ \hline
\end{tabular} \\
\vspace{4mm} \\
Table 3: latency result on idle setup, in \textmu s\\
\vspace{4mm} \\
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular}{|l|c|r|r|}
\hline
\multirow{2}{*}{} & \multicolumn{3}{c|}{user} \\ \cline{2-4} 
 & min & \multicolumn{1}{c|}{avg} & \multicolumn{1}{c|}{max} \\ \hline
Xenomai 2 & 9.291 & 18.666 & 41.624 \\ \hline
Xenomai 3 & 8.296 & 18.406 & 44.644 \\ \hline
& \multicolumn{3}{c|}{kernel}       \\ \hline
Xenomai 2 & 6.584 & 10.833 & 30.588 \\ \hline
Xenomai 3 & 5.334 & 9.424 & 27.564  \\ \hline
& \multicolumn{3}{c|}{timer-irq}    \\ \hline
Xenomai 2 & 2.089 & 2.927 & 14.430  \\ \hline
Xenomai 3 & 2.544 & 3.246 & 18.026  \\ \hline
\end{tabular} \\
\vspace{4mm} \\
Table 4: latency result on cpu-stressed setup, in \textmu s\\
\vspace{4mm} \\
%%%%%%%%%%%%%%%%%%%%%%%%%
